Multi-stage programming with functors and monads: eliminating abstraction overhead from generic code

### 2007-07-11 SCP2008/paper/metamonads.tex
finish 2nd subsection, start 3rd.  Add references

>>>>

Our overall approach can best be described a combination 
of two approaches: hand-writing a code generator (cogen) suitable
for multi-level specialization \cite{Gluck95,GluckJ97} and creating
an embedded domain-specific language (EDSL) \cite{edsl,WhenHowDSL}.
More specifically we start from a \emph{known} set of implementations
of an algorithm, and extract commonalities and variation points.
This is unlike~\cite{journals/tse/Parnas76} and most subsequent
approaches to product families, as we do not over-engineer our design
by imagining weird variations that are unlikely to come up in realistic
situations, but only create variations when we notice them in actual use.
This approach is quite well-suited to the development of scientific
software, which has a rich history and where most useful variations have
already appeared in some form.

\jacques{need to describe actual process a bit more, maybe one or two
paragraphs, and then this section is done}
